Multispecies survey for diet comp

### 2020-12-03 SurveyDietCompTest.Rmd
random proportion to unid category

  # check for GroupType or InvertType
  if (!("grouptype" | "inverttype") %in% colnames(fgs)) {
    stop(paste("The columns GroupType or InvertType ars not in your functional\n",
      "groups file."))
  }

@@

>>>>

  # check for GroupType or InvertType
  if (!("grouptype" %in% colnames(fgs) | "inverttype"%in% colnames(fgs))) {
    stop(paste("The columns GroupType or InvertType ars not in your functional\n",
      "groups file."))
  }

@@

  # associate prey categories (atlantis user guide I Table 8) with unid categories
  fgs<- fgs%>% 
       mutate(unidtype = case_when((grouptype %in% c("mammal", 
                                                     "bird", 
                                                     "reptile")) ~ "Unid_Vert",
                                   (grouptype %in% c("fish", 
                                                     "shark")) ~ "Unid_Fish",
                                   (grouptype %in% c("fish_invert", 
                                                     "cep", 
                                                     "pwn", 
                                                     "lg_inf",
                                                     "sm_inf",
                                                     "sed_ep_ff",
                                                     "sed_ep_other",
                                                     "mobile_ep_other",
                                                     "coral",
                                                     "sponge")) ~ "Unid_Invert",
                                   (grouptype %in% c("lg_zoo", 
                                                     "med_zoo", 
                                                     "sm_zoo",
                                                     "dinoflag",
                                                     "lg_phy",
                                                     "sm_phy")) ~ "Unid_Plankton",
                                   TRUE ~ "Unid"))

  # associate prey with prey category
  # randomly assign up to unidprey % of prey in each prey category to associated unid category

  fgsprey <- fgs[,c("name", "unidtype")]
  names(fgsprey)[names(fgsprey) == 'name'] <- 'prey'

  dat2 <- left_join(dat2, fgsprey) %>%
    group_by(species, time.days, agecl, prey) %>%
    mutate(unidprop = runif(1, 0, unidprey*atoutput))

  # add rows with unid categories and sum prop assigned to the category
